%----------------------------------------------------------------
\cvsection{Employment}

%----------------------------------------------------------------
\begin{cventries}
	\cventry
	{Senior mobile developer, Product Development, Mobile Solutions}
	{\href{https://www.careers.fiserv.com/new-zealand}{Fiserv. New Zealand}}
	{Auckland,\enskip New Zealand}
	{Oct 2014 – Present}
	{
		\begin{cvitems}
			\item {Developed dynamic brandable \href{https://play.google.com/store/apps/details?id=com.fiserv.touchbankingasp&hl=en}{\color{deepblue}{Android}}/\href{https://itunes.apple.com/us/app/touchbanking/id386678211?mt=8}{\color{deepblue}{iPhone}} online banking App}
			\item {Developed custom branded online banking Apps}
			\item 
			{Main responsibilities are: 
				\\\tab * Software delivery and maintenance.
				\\\tab * Responsible for any Android work, defect fix, and product support.
				\\\tab * Reduce code warnings, improve test coverage, and code review.
				\\\tab * Supervising and improve code quality, test coverage.
				\\\tab * Investigate new Mobile technologies and tools.
				\\\tab * Raise proposal that benefits to project.
				\\\tab * Guide the new comers and knowledge sharing.
				\\\tab * Support and work with different teams
				\\\tab * Supervising modularization
			}
			\item {Lead / go-to person of recent Android work: 
				\\\tab FCM Push Notification, Router / Deeplinks, Modularization, DI (Hilt), EventBus, Dark theme / Dynamic branding, Biometrics login, Clean Architecture
				\\\tab Remote Deposit Capture (Camera), ePayments, ...}
			\item {Involved in features: 
				\\\tab DI (Guice), Modularization, Authentication, Camera2, Transfer, Payments, Location, Calendar, Quick links, Cards, ...}
			\item {Played with tools, and languages in Fiserv: 
				\\\tab Android Studio, Jenkins, Fastlane, Git, Kotlin, Java, JavaScript, Groovy, Python, Bash, Flutter, ...}
		\end{cvitems}
	}
\end{cventries}

%----------------------------------------------------------------
\begin{cventries}
	\cventry
	{Android developer}
	{Freelance}
	{Auckland,\enskip New Zealand}
	{Aug 2014}
	{
		\begin{cvitems}
			\item {Developed independently by Go for Android \href{https://play.google.com/store/apps/details?id=com.gmail.jiangyang5157.sudoku}{\color{deepblue}{Sudoku}} game App development\\
			Knuth's Algorithm X based runtime Sudoku puzzle generator;\enskip
			Efficiency at the millisecond level, strong random and unique solution}
		\end{cvitems}
	}
\end{cventries}

%----------------------------------------------------------------
\begin{cventries}
	\cventry
	{Android developer}
	{Freelance for \href{http://www.english119.cn}{PerfectEnglish}}
	{Guangzhou,\enskip Guangdong,\enskip China}
	{Mar 2012 – Apr 2012}
	{
		\begin{cvitems}
			\item {Developed independently for Android \href{http://shouji.baidu.com/software/11415668.html}{\color{deepblue}{PerfectEnglish}} App development\\
			Video player,\enskip Subtitle calibration,\enskip Voice recorder;\enskip Vocabulary study by Ebbinghaus forgetting curve,\enskip Dictionary service}
		\end{cvitems}
	}
\end{cventries}

%----------------------------------------------------------------
\begin{cventries}
	\cventry
	{Android developer, Operating Systems Development section, Research and Development department}
	{\href{http://www.inventec.com/english/indexEN.htm}{Inventec Co. Ltd.}}
	{Shanghai,\enskip China}
	{Nov 2009 – Dec 2011}
	{
		\begin{cvitems}
			\item {\href{http://www.androidcentral.com/android-powered-dr-eye-makes-its-debut}{\color{deepblue}{Dr.eye}} mini netbook build-in Android Apps development\\
			\href{https://play.google.com/store/apps/details?id=com.inventec.dreye.dictnew}{\color{deepblue}{Dr.eye Dictionary}}, Multimedia ebook, TOEIC Online, Weather App \& widget}
			\item {Client customized Dr.eye Dictionary:\enskip
			Dictionary for HTC,\enskip 
			Dictionary for Asus Android 3.1 Tablet,\enskip
			Dictionary for Foxconn}
			\item {RED5 video chat research}
		\end{cvitems}
	}
\end{cventries}

%----------------------------------------------------------------